Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward

### 2022-06-22 analysis/paper/paper.Rmd
clarify writing and remove double citation

The models' were structured as follows to predict two responses, the availability of computational methods and data that were created or collected for the manuscript.
To predict the responses with publishing journal (abbreviation was used throughout) the formula took the form: response ~ abbreviation and the models included assignee as a random effect (formula: ~1 | assignee).
To predict the response with year were predicted as (formula: response ~ year) and the models included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).
To predict the responses with IF_5year the formula took the form response ~ IF_5year and included assignee as random effect (formula: ~1 | assignee) without journal as a random effect to mitigate correlation between impact factor and the journal of publication.

@@

Model fitness's were evaluated using model summaries and diagnostic plots from 'brms' (version `r packageVersion("brms")`) [@Burkner2017; @Burkner2018; @Burkner2021] and posterior fits using `pp_check()` (Figure \@ref(fig:posteriors)) from the contributed R package 'bayesplot' (version `r packageVersion("bayesplot")`) [@Gabry2019].

>>>>

The models' were structured as follows to predict two responses, the availability of computational methods and data that were created or collected for the manuscript.
To predict the responses with publishing journal, as the journals' abbreviation, the formula took the form: response ~ abbreviation and the models included assignee as a random effect (formula: ~1 | assignee).
To predict the response with year were predicted as (formula: response ~ year) and the models included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)).
To predict the responses with IF_5year the formula took the form response ~ IF_5year and included assignee as random effect (formula: ~1 | assignee) without journal as a random effect to mitigate correlation between impact factor and the journal of publication.

@@

Model fitness's were evaluated using model summaries and diagnostic plots from 'brms' (version `r packageVersion("brms")`) and posterior fits using `pp_check()` (Figure \@ref(fig:posteriors)) from the contributed R package 'bayesplot' (version `r packageVersion("bayesplot")`) [@Gabry2019].
